Search-based Synthesis of Network Intrusion Detection Rules

### 2019-10-02 paper/paper.tex
minor comments

\begin{table*}[t!]
  \caption{\label{table:attacks}Characterization of attacks analyzed
    and Golden Rule of Suricata (reference) to capture it.}  
  \centering
  \begin{tabular}{lllll}
    \toprule
    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Protocol} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{Golden Rule} \\
    \midrule
    GET/POST Flood & multiple & HTTP & Denial of Service & - \\      
    Ping Scan & single & ICMP & Discovers active hosts in a network &  - \\
    Black Nurse & multiple & ICMP & Denial of Service & - \\
    Ping Flood  & multiple & ICMP & Denial of Service & - \\  
    Port Scan TCP & single & TCP & Discovers open ports in a host & -  \\
    SYN Flood & multiple & TCP & Denial of Service & - \\
    Port Scan UDP & single & UDP & Discovers open ports in a host & - \\        
    \bottomrule
  \end{tabular}
\end{table*}

@@

Note from the figure that the negative traffic is an input to the
technique. The positive traffic, in contrast, is not. \tname{} uses
public databases storing different kinds of positive traffic for all
protocols covered by Suricata. \Fix{what databases?}

>>>>

\begin{table*}[t!]
  \caption{\label{table:attacks}Characterization of attacks analyzed
    and Golden Rule of Suricata (reference) to capture it.\Mar{please,
  show me the Golden Rule, \ie{} the part that is relevant of each rule (for
  capturing the negative traffic precisely)}}  
  \centering
  \begin{tabular}{lllll}
    \toprule
    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Protocol} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{Golden Rule} \\
    \midrule
    GET/POST Flood & multiple & HTTP & Denial of Service & - \\      
    Ping Scan & single & ICMP & Discovers active hosts in a network &  - \\
    Black Nurse & multiple & ICMP & Denial of Service & - \\
    Ping Flood  & multiple & ICMP & Denial of Service & - \\  
    Port Scan TCP & single & TCP & Discovers open ports in a host & -  \\
    SYN Flood & multiple & TCP & Denial of Service & - \\
    Port Scan UDP & single & UDP & Discovers open ports in a host & - \\        
    \bottomrule
  \end{tabular}
\end{table*}

@@

Note from Figure~\ref{fig:overview} that the negative traffic is an
input to the technique. The positive (non malicious) traffic, in
contrast, is not. \tname{} uses public databases storing different
kinds of positive traffic for all protocols covered by Suricata. We
used two datasets of positive traffic. The Bigflows.pcap dataset is
part of the TcpReplay~\cite{tcpreplay} open source project. This
dataset includes real network traffic on a busy private network access
point to the Internet. According to the TcpReplay web site ``This
capture is much larger and has a smaller average packet size than the
previous capture (smallFlows.pcap). It also has many more flows and
different applications.''. In addition to the Bigflows.pcap dataset,
we also used datasets of normal traffic made available by Stratosphere
Lab~\cite{stratosphere-normal}.

%% \Gui{We are using the bigflows.pcap provided by tcpreplay on http://tcpreplay.appneta.com/wiki/captures.html "This is a capture of real network traffic on a busy private network’s access point to the Internet"
%%  }
